### 2012-09-29 abstract.tex
shortened abstract

Tennis is a hugely popular sport around the globe. Its fans include
not only spectators attracted by the excitement of the game but also
speculators attracted by the possibility of making large financial
gains.  Indeed, every on-court development drives the movement of
several in-play financial markets.

As in other financial markets, sophisticated traders make use of
quantitative models in an attempt to gain an advantage over their
peers. For a tennis singles match, the models are usually based on
hierarchical Markov chains and typically yield the probability of each
player winning the match as a function of three parameters: the
current score, and the probability of each player winning a point on
their serve.

These models, however, ignore the potential impact of retirement risk
due to injuries, which can drastically alter in-play betting odds~--
even during the course of a single point. The exact nature of the
impact on a given market depends on the payout policy of that market
in the case of player retirement.

This paper proposes novel quantitative models which reflect the
in-play evolution of retirement risk due to injury and the
corresponding impacts on in-play financial markets based on match
outcome under different retirement payout policies. Injuries are
assumed to occur according to a Bernoulli process, with a magnitude
sampled from a truncated exponential distribution. Retirement risk is
propagated from one point to another subject to a damping parameter
that reflects a player's ability to ``run off'' an injury.

In terms of practical deployment, a challenging problem is to
correctly parameterise the models given the availability of a current
score feed and odds data in two match outcome markets with different
retirement policies. Artificially generated match data shows that it
is possible to infer model parameters effectively. We also find that
we are able to follow the progression of Betfair in-play tennis
markets for a number of real-life matches to a good degree of accuracy
and can provide a value for the retirement risk of a given player at
any point.  It is also possible to predict the evolution of
match outcome markets that feature other retirement policies.

>>>>

Tennis attracts both spectators and speculators.  Indeed, every
on-court development impacts on in-play financial markets.  For
singles matches, sophisticated traders make use of quantitative
models.  These yield the probability of each player winning the match
given the current score and the probability of each player winning a
point on serve.  Significantly, these models ignore retirement risk,
which can drastically and rapidly alter in-play odds. The precise
impact on a market depends on that market.s payout policy in the case
of player retirement.

This paper proposes novel quantitative models for the in-play
evolution of retirement risk due to injury and the corresponding
impacts on in-play match outcome markets under different retirement
payout policies. Injury occurrence is assumed to be a Bernoulli
process, with a magnitude sampled from a truncated exponential
distribution. Retirement risk is propagated from one point to another
subject to a damping parameter that reflects a player's ability to
``run off'' an injury.

An important practical challenge is to parameterise our models given a
score feed and odds data for two match outcome markets with different
retirement policies. We demonstrate the feasibility of not only
inferring model parameters from synthetic data effectively but also of
mimicking real in-play markets.
